PWNCAT2

### 2012-06-07 pwncatalog/PWNCAT2/paper/subsections/off_peak_phase_selection.tex
update

Set the ncpPrior parameter to 5?

@@

How to implement Baysian blocks on periodic data.

\begin{figure}
  \ifdefined\bwfigures
  \plotone{off_peak_select_bw.eps}
  \else
  \plotone{off_peak_select_color.eps}
  \fi
  \caption{Off peak selection for some pulsars\dots}
  \label{fig:off_peak_select}
\end{figure}

>>>>

\todo[inline]{This is just a placeholder. Hopefully Andrea can fill this section
in with the real details.}

\todo[inline]{How to implement Baysian blocks on periodic data.}

@@

\begin{figure}
  \ifdefined\bwfigures
  \plotone{off_peak_select_bw.eps}
  \else
  \plotone{off_peak_select_color.eps}
  \fi
  \caption{Off peak selection for some pulsars. 
  \todo[inline]{This is just a placeholder figure. 
  Hopefull Andrea or somebody can update the plot
  once the real algorithm is finished.}}
  \label{fig:off_peak_select}
\end{figure}
